### 2017-12-18 manuscript.rmd
fixed a citation in the rmd, did not rebuild pdf

The first study, Kryuchkova-Mostacci and Robinson-Rechavi (KMRR) [@KryuchkovaMostacci:2016iw], analyzed multiple vertebrate expression datasets to test the ortholog conjecture - the hypothesis that orthologs tend to have more conserved attributes (specificity of expression across organs in this case) than do paralogs [@Nehrt:2011bm, @Koonin:2005fp]. Using pairwise comparisons (Fig. 1*A*), they found lower expression correlation between paralogs than between orthologs and interpreted this as strong support for the ortholog conjecture.

>>>>

The first study, Kryuchkova-Mostacci and Robinson-Rechavi (KMRR) [@KryuchkovaMostacci:2016iw], analyzed multiple vertebrate expression datasets to test the ortholog conjecture - the hypothesis that orthologs tend to have more conserved attributes (specificity of expression across organs in this case) than do paralogs [@Nehrt:2011bm; @Koonin:2005fp]. Using pairwise comparisons (Fig. 1*A*), they found lower expression correlation between paralogs than between orthologs and interpreted this as strong support for the ortholog conjecture.
